### 2022-11-12 project_Antonio/paper.tex
Add files via upload

\def\Student{Antonio Paredes Sotelo}
\def\Title{THESIS PROJECT PROPOSAL}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{}
\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}

@@

	\vspace{2cm}
        \begin{adjustwidth}{2cm}{2cm}{
            TITLE:\par
            {\large \ProjectTitle \par}
          }
        \end{adjustwidth}

	\vspace{0.5cm}
        \begin{adjustwidth}{2cm}{2cm}{
            RESEARCH LINE: \par
            \ResearchLine \par}
        \end{adjustwidth}

@@

  \begin{center}
    {\Large \ProjectTitle \par}
    \vspace{1cm}
    {\itshape\textbf{Abstract}\par}
  \end{center}

@@

\onehalfspacing This research project proposes to study the unobserved decays modes of the Higgs boson. \iffalse associated with a single top quark (tH) using Higgs boson decay to multilepton final state \fi The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$. Serches for decays of the Higgs boson into pairs of $J$

Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode. The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations. Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb. We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$. \par

\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.

For these studies the data of the LHC Run 2

@@

There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
production in association with vector boson (VH, V = $W^{\pm}$ or Z), Higgs production with top quark and top anti-quark ($t\bar{t}H$) and Higgs 
production in association with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs boson at LHC is 
gluon gluon fusion (ggF). As bosons like gluons and photons are massless, they do not interact directly with the Higgs boson 
and processes like ggF or Higgs boson decay to pair of photons are not possible at tree level and can only proceed via loop 
diagrams which involve $W^{\pm}$ boson, top quark or bottom quark in the loop. The Higgs boson can also decay to other particles and these decay 
channels have different branching ratios which are computed using the partial decay widths. Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom quarks, 
muons and electrons. Higgs boson can also decay to Z boson and a photon. The important SM Higgs Boson production modes are shown in Figure 2. The production cross section and branching ratios of various decay channels of Higgs boson are shown in Figure 3.

%\afterpage{
\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{./pg.png}
	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
	\label{figure 2}
\end{figure}

@@

The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
\begin{itemize}
\item{Fine structure constant $\alpha$},
\item{Weinberg angle or the weak mixing angle $\theta_W$},
\item{The coupling constant of strong interaction $\alpha_s$},
\item{Electroweak symmetry breaking energy scale v},
\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
\end{itemize}
 The fine 
tunings related to the Higgs 
mass and the free parameters in SM suggests new physics beyond Standard model (BSM). There are lot of specific 
BSM theories and most of these 
models involve new heavy particles. In order to identify which new physics lies beyond the 
electroweak (EW) scale, the new parameters 
of such theories may be constrained by the actual low energy experiments.

There is another approach immitating 
Fermi's treatment of beta decay 
which consists of considering the SM as the first order approximation of the actual theory 
and by completing it with a series 
of higher dimensional operators. When the electroweak symmetry breaking takes place well 
below the mass of the new particles, 
the BSM physics is taken into account at the EW scale and below by adding higher dimensional 
operators to the SM Lagrangian. 
They are built out of SM fields and supposed to be invariant under its gauge group which is $SU(3)_C \times SU(2)_L \times U(1)_Y$.
%Those 
%operators are the low-energy residue 
%of the high energy theory. This approach does not pretend to guess the complete high-energy 
%model and it is based solely on 
%the symmetry of the  theory. The operators are general and the only model dependence is 
%encoded in the size of the operator
%coefficients, which is to be set from experiments. The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
%model predictions if these higher 
%dimensional operators are present in low energy effective SM theory. We can consider 
%anomalous Higgs and Higgs-gauge effective 
%dimension 6 operators like $-\frac{1}{3}(\phi^{\dagger}\phi)^3$, $\frac{1}{2} \partial_{\mu} 
%(\phi^{\dagger} \phi) 
%\partial^{\mu}(\phi^{\dagger} \phi)$ and $(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} 
%(D^{\mu} \phi)$ to calculate the 
%deviation of Higgs boson-fermion couplings from SM. The first operator $-\frac{1}{3}(\phi^{\dagg%er}\phi)^3$ shift the minimum of 
%the Higgs potential. Also as there 
%will be rescaling of the Higgs field due to the introduction of these operators in the 
%potential term, Higgs-fermion (quarks 
%and leptons) couplings will be modified.
%The yukawa coupling of top quark with Higgs boson will be modified due to the presence of such higher dimensional operators.

\iffalse
\begin{figure}[ht]
	\centering
	\includegraphics[width=\columnwidth]{./cms.png}
	\caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
	\label{figure 4}
\end{figure}
\fi

\iffalse
The production of Higgs boson in association with single top quark is one of the rare Higgs 
boson production mode \cite{sirunyan2019search}. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products 
unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most 
probable decay of the top quark is 
into bottom (b) quark and $W^{\pm}$ boson \cite{{Tanabashi:2018oca}}. Using b-jet tagging algorithms, the jet originating from 
b-quark can be reconstructed to 
identity the top quark. In SM, the couplings of the Higgs boson to fermions (quarks and leptons) known as Yukawa couplings are proportional to the mass 
of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
which means that out of all known 
quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
coupling $y_t$ \cite{Aad_2016}. That is why the 
Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 
deviation from standard model prediction might give an indication of new physics. The two 
processes at LHC which will allow us to directly probe the Yukawa 
coupling between Higgs boson and top quark are Higgs boson production in association with top 
quark pair ($t\bar{t}H$) via 
strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
occur via electroweak interaction, it 
is more rare than t$\bar{t}$H production \cite{Sirunyan:2018ygk}. The Higgs boson in the tH channel can be radiated 
off by a $W^{\pm}$ boson or by a top quark as shown in Figure 4.

These two processes in standard model have destructive interference which allow us to 
probe the relative sign between 
the coupling of top quark with Higgs boson $y_t$ and the coupling of $W^{\pm}$ boson to the Higgs 
boson $g_{HWW}$ \cite{Sirunyan:2018lzm}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
production cross section which is a special property of tH production channel making it an 
interesting production channel to probe using LHC 2016, 2017 and 2018 data \cite{farina2013lifting}. The coupling 
strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
us the deviation of $y_t$ from the SM prediction.

The LHC is sensitive to an anomalous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. 
The anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential.
As there is strong destructive inteference in the t-channel for the standard model  couplings, this production mode is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs  boson and top quark induced by higher dimensional operators in effective beyond SM theory \cite{sirunyan2019search}.
\fi

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years. The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC). It is designed to detect particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum. A silicon tracker, made of about 75 
million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}. The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).

@@

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.9\columnwidth]{./lum6.png}
    \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
    \label{figure6}
  \end{figure}
  \clearpage

@@

LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
 The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt} \cite{Sirunyan:2018lzm}.
Multilepton final states like ee, $\mu\mu$ and $e\mu$ and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result. The data slightly favor positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
\newpage
%\afterpage{
  \begin{figure}[H]
    \centering
    \includegraphics[scale=0.4]{./couplings.png}
    \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
    \label{figureKappas}
  \end{figure}

@@

\newpage
\section{PROPOSAL}

@@

\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory. For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results. An observation of such decay  with this sample would indicate the presence of physics beyond the standard model. It is also expected to estimate projections of the sensitivity to the High Luminosity phase of the LHC (HL-LHC) (2026-2036) which will accumulate up to 100 times the data used for current measurements.

@@

%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..

@@

\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles. Through this project we will investigate the decay of the Higgs boson to $J/\psi$ in proton-proton collisions with the CMS experiment at the LHC. The decay to $J/\psi$ has not been observed so far.

@@

\onehalfspacing Studies about the decay of the Higgs boson production channel have already started within the CMS and ATLAS collaboration and publications are based on data from the 2011-2012 run and some data from the second run of 2015-2016.
In these results, there was no evidence of signal and upper limits were set on the production cross-section.
The current results combine three types of searches: H$\rightarrow WW/ZZ/\tau\tau \rightarrow$leptons, H$\rightarrow\gamma\gamma$, and H$\rightarrow b\bar{b}$.
%The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, the current data almost rules out this model.

With this project we propose to incorporate the full Run 2 dataset corresponding to 150 fb$^{-1}$.
A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties.
This mean that the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be excluded.

Additionally, in subsequent phases of the LHC (2021-2023 and 2026-2038) the amount of data will increase by a factor of up to 100, which implies the upper limit for the SM case will reduce to about 2.6 times the expected cross-section. This implies that even for the HL-LHC it will be difficult to observe the tH production, but at the same time more and more phase space of BSM models will be excluded.

\iffalse
In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}H$ production because the cross-section of $t\bar{t}H$ is much larger than that of tH and some events pass the selections designed for tH.
The fraction of tH events over tH + $t\bar{t}H$ is currently only 5$\%$ with the analysis techniques used.
We expect to improve the analysis techniques using multi-variate techniques, for example boosted decision trees or other algorithms, to improve the identification of signal events over the rest of the backgrounds.
This will provide additional improvements in the limits and a possible observation of the SM signal as well as stringent exclusions for BSM models.
\fi

@@

In order to complete a journal publication of a  
%measurement of tH production using one of these channels, several aspects  must be worked on:
\begin{itemize}
\item Simulation of the signal events using Monte Carlo generators which implement the theoretical model.
\item Implementation of event reconstruction and selection algorithms which select high quality signal events and reduce the background events to a minimum.
\item Studies of lepton and jet identification algorithms which improve the background rejection.
\item Due to the small signal over background ratio, a multi-variate algorithm is employed which combines different event variables and exploits the correlations to construct a final discriminant. This algorithm must be trained using simulated signal and background events.
\item A model for the observed data must be constructed from the known background processes. These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
\item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
\item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal or in the absence as a limit. Further analysis is required to place constraints on paramater space of BSM models.
\end{itemize}

In addition to the above objectives, members of the CMS collaboration are expected to participate in the detector operation and upgrade activities (or service work).
During shut-down periods, these activities include testing and installation of new detectors.
During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
In addition to the data analysis plans described before, another objective is to contribute in one of the developments of the CMS detector to  prepare for the HL-LHC phase.
%

Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.

@@

\onehalfspacing The methods for a measurement of the 
%coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.

Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
However, the members of the CMS collaboration must monitor the quality and rate of proton collisions at the interaction point at the center of the detector in order to collect a high quality dataset which can be stored for many years to do analysis.
Calibration and maintenance of all parts of the detector is necessary in order to achieve close to $100\%$ particle detection efficiency and noise levels to a minimum. This work is achieved by participating in the detector operation groups and performing data acquisition shifts during run time.  
Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities.

@@

>>>>

\def\Student{Antonio Paredes Sotelo}
\def\Title{Anteproyecto}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
\def\ProjectTitle{B\'usqueda de part\'iculas de Higgs con modelos de f\'sica m\'as all\'a del Modelo Est\'andar y medici\'on de la luminosidad usando el m\'etodo de Pixel Cluster Counting en el experimento CMS del CERN}
\def\ProjectTitleEnglish{Search for Higgs bosons using models of physics beyond the Standard Model and measurement of luminosity using the Pixel Cluster Counting method in the CMS experiment at CERN}
\def\ResearchLine{F\'{i}sica Matematicas}

@@

	\vspace{1cm}
        \begin{adjustwidth}{2cm}{2cm}{
            T\'ITULO:\par
            {\large \ProjectTitle \par}
          }
          \end{adjustwidth}

        \vspace{0.5cm}
        \begin{adjustwidth}{2cm}{2cm}{
            TITLE:\par
            {\large \ProjectTitleEnglish \par}
          }
          \end{adjustwidth}

	\vspace{0.5cm}
        \begin{adjustwidth}{2cm}{2cm}{
            RESEARCH LINE (LGAC):  \par
            \ResearchLine \par}
        \end{adjustwidth}

@@

  \begin{center}
    {\Large \ProjectTitleEnglish \par}
    \vspace{1cm}
    {\itshape\textbf{Abstract}\par}
  \end{center}

@@

\onehalfspacing This research project proposes to study the unobserved decays modes of the Higgs boson. \iffalse associated with a single top quark (tH) using Higgs boson decay to multilepton final state \fi The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$. Serches for decays of the Higgs boson into pairs of $J/\psi$ or $\Upsilon$.

%Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode. The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations. Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb. We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$. \par

%\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory.

%For these studies the data of the LHC Run 2

@@

There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
production in association with vector boson (VH, V = $W^{\pm}$ or Z), Higgs production with top quark and top anti-quark ($t\bar{t}H$) and Higgs 
production in association with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs boson at LHC is 
gluon gluon fusion (ggF). Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom quarks, 
muons and electrons. Higgs boson can also decay to Z boson and a photon. The important SM Higgs Boson production modes are shown in Figure 2. The production cross section and branching ratios of various decay channels of Higgs boson are shown in Figure 3.
Figure 3 also show the main decays channels by the SM.

%\afterpage{
\begin{figure}[H]
	\centering
	\includegraphics[width=\columnwidth]{./production_mode.png}
	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH in proton collisions.}
	\label{figure 2}
\end{figure}

@@

The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM. There are lot of specific 
BSM theories and most of these models involve new heavy particles. In order to identify which new physics lies beyond the 
electroweak (EW) scale, the new parameters  of such theories may be constrained by the actual low energy experiments. \\ 
%The fine tunings related to the Higgs mass and the free parameters in SM suggests new physics beyond Standard model (BSM).

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years. The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC). It is designed to detect particles known as muons very accurately. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM). \\

The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum. A silicon tracker, made of about 75 
million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}. The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.

@@

  \begin{figure}[H]
    \centering
    \includegraphics[width=0.9\columnwidth]{./lum6.png}
    \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
    \label{figure6}
  \end{figure}

@@

LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS. The luminosity delivered by the LHC during Run 1 (2011-2012),  Run 2 (2015-2018), and the expected luminosity for Run 3 and HL-LHC is shown in Figure 5.

\clearpage
\iffalse
The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).

This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.

Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt} \cite{Sirunyan:2018lzm}.
Multilepton final states like ee, $\mu\mu$ and $e\mu$ and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result. The data slightly favor positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.

\newpage
%\afterpage{
  \begin{figure}[H]
    \centering
    \includegraphics[scale=0.4]{./couplings.png}
    \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
    \label{figureKappas}
  \end{figure}

@@

\newpage
\fi
\section{PROPOSAL}

@@

\onehalfspacing In this project, it is proposed to search for the decays of the Higgs boson to pairs of $J/\psi$ or $\Upsilon$ in the CMS detector based at the Large Hadron Collider of the CERN laboratory. For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results. Previously CMS has carried out studies with the data from 2017 \cite{2019134811} corresponding to 37.5 fb$^{-1}$ and ATLAS in 2015 \cit{Aad_2015}.

%It is also expected to estimate projections of the sensitivity to the High Luminosity phase of the LHC (HL-LHC) (2026-2036) which will accumulate up to 100 times the data used for current measurements.

@@

\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles. Through this project we will investigate the decay of the Higgs boson to pairs of $J/\psi$ or $\Upsilon$ in proton-proton collisions with the CMS experiment at the LHC. An observation of such decay  with this sample would indicate the presence of physics beyond the standard model. The decay to pairs of $J/\psi$ or $\Upsilon$ has not been observed so far. An observation of such decay  with this sample would indicate the presence of physics beyond the standard model.

@@

@@

% Studies about the decay of the Higgs boson have already started within the CMS and ATLAS collaboration and publications are based on data from the 2011-2012 run and some data from the second run of 2015-2016.

\onehalfspacing With the CMS search mentioned above using 2017 data, an upper limit of $1.8 \times 10^{-3}$ was obtained in the $J/\psi$ pair while in the $\Upsilon$ pair channel, the limit was $1.4 \times 10^{-3}$.

With this project we propose to incorporate the full Run 2 dataset corresponding to 150 fb$^{-1}$.
A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties. In case of observing a signal with this data this would mean evidence of physics beyond the standard model.

\iffalse
Additionally, in subsequent phases of the LHC (2021-2023 and 2026-2038) the amount of data will increase by a factor of up to 100, which implies the upper limit for the SM case will reduce to about 2.6 times the expected cross-section. This implies that even for the HL-LHC it will be difficult to observe the tH production, but at the same time more and more phase space of BSM models will be excluded.

%these were the results
%The currently published result \cite{} uses 37.5 fb$^{-1}$ of collision data and obtains 
%CMS collaboration has perfomed
%pairexpected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
%The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
%The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
%In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, the current data almost rules out this model.

%This mean that the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be excluded.
In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}H$ production because the cross-section of $t\bar{t}H$ is much larger than that of tH and some events pass the selections designed for tH.
The fraction of tH events over tH + $t\bar{t}H$ is currently only 5$\%$ with the analysis techniques used.
We expect to improve the analysis techniques using multi-variate techniques, for example boosted decision trees or other algorithms, to improve the identification of signal events over the rest of the backgrounds.
This will provide additional improvements in the limits and a possible observation of the SM signal as well as stringent exclusions for BSM models.
\fi

@@

In order to complete a journal publication of this search the following are need it:
%production using one of these channels, several aspects  must be worked on:
%of these search
\begin{itemize}
\item Simulation of the signal events using Monte Carlo generators which implement the theoretical model.
\item Implementation of event reconstruction and selection algorithms which select high quality signal events and reduce the background events to a minimum.
\item Studies of lepton algorithms which improve the background rejection.
\item Due to the small signal over background ratio, a multi-variate algorithm is maybe employed which combines different event variables and exploits the correlations to construct a final discriminant. This algorithm must be trained using simulated signal and background events.
\item A model for the observed data must be constructed from the known background processes. 
%These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
\item Reconstruction of $J/\psi$ and $\Upsilon$ with two muons \cite{Khachatryan_2014,Sirunyan_2018}.
\item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
\item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal or in the absence as a limit. %Further analysis is required to place constraints on paramater space of BSM models.
\end{itemize}

In addition to the above objectives, members of the CMS collaboration are expected to participate in the detector operation and upgrade activities (or service work). During shut-down periods, these activities include testing and installation of new detectors.The luminosity data of run 3 will be studied and a luminosity measurement is planned for run 3. For run 2 we have these results \cite{CMS-PAS-LUM-17-004,CMS-PAS-LUM-18-002}.

%During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
%In addition to the data analysis plans described before, another objective is to contribute in one of the developments of the CMS detector to  prepare for the HL-LHC phase.
%

%Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.

@@

%\onehalfspacing The methods for a measurement of the 
%coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.

\onehalfspacing Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
However, the members of the CMS collaboration must monitor the quality and rate of proton collisions at the interaction point at the center of the detector in order to collect a high quality dataset which can be stored for many years to do analysis.
Calibration and maintenance of all parts of the detector is necessary in order to achieve close to $100\%$ particle detection efficiency and noise levels to a minimum. This work is achieved by participating in the detector operation groups and performing data acquisition shifts during run time.  
Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities.

@@

Luminosity is one of the most omportant parameter for a particle accelerator. It is the measure of number of proton-proton collisions occurring in unit centimetre square area per second. The installation of the CMS Phase-1 pixel detector took place during the extended year-end technical stop of the LHC in 2016/2017. The CMS Phase-1 pixel detector consists of four concentric barrel layers anf three disks. The CMS Phase-1 pixel detector is built from 1856 segmented silicon sensor modules,
where 1184 modules are used in the barrel pixel detector (BPIX) and 672 modules are used for the forward disks (FPIX). Each module consists of a sensor with 160x416 pixels connected to 16 readout chips (ROCs).One of the systems used for measuring luminosity at CMS is a technique called Pixel Cluster Counting (PCC) method. The PCC method uses the rate of pixel clusters in the CMS pixel detector to provide an luminosity measurement.
